\documentclass[a4paper,12pt]{article}
\usepackage[top=12ex, bottom=12ex, left=9ex, right=9ex,showframe=false]{geometry}
\linespread{1.8}
\usepackage[ampersand]{easylist}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{ \fancyplain{}{Yuhao Yang} }
\rhead{ \fancyplain{}{\leftmark} }
\cfoot{ \fancyplain{}{\thepage} }
\usepackage[unicode]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{pifont}
\usepackage{fourier}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{extarrows}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{arrows,positioning,calc,fadings,shapes,decorations.markings}
\usepackage{array}
\usepackage{anyfontsize}
\usepackage{indentfirst}
\usepackage{ulem}
\usepackage{paralist}
\usepackage{enumitem}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{wrapfig}
\usepackage{xfrac}

% % % % % % % % % %

% font type
\renewcommand*\rmdefault{ppl}
%\newcommand{\dd}{\mathrm{d}}
%\newcommand{\ee}{\mathrm{e}}

% % % % % % % % % %

\renewcommand\thefootnote{\textcolor{blue}{[\arabic{footnote}]}}
\hypersetup{
    colorlinks, linkcolor={purple}, citecolor={blue}, urlcolor={blue},
    pdftitle={Cambridge International A-Level Physics Course Handout},
    pdfauthor={Yuhao Yang},
    pdfsubject={A-Level Physics} }

% tikz arrows
\tikzset{>=stealth', pil/.style={ ->, thick, shorten <=2pt, shorten >=2pt,} }

% tikz decription node style
\tikzset{note/.style={rectangle, rounded corners, minimum size=6mm, draw=black, fill=white, font=\itshape, align=center,execute at begin node=\setlength{\baselineskip}{1.2em}}}
\tikzset{graphlabel/.style={postaction={decorate,transform shape, decoration={markings, mark=at position .5 with \node #1;}}}}

% % % % % % % % % % %

% example environment
\newcounter{example}[section]
\renewcommand{\theexample}{\arabic{section}.\arabic{example}}

\newcommand{\example}[1]{\refstepcounter{example}
	\vspace*{0.5\baselineskip}\noindent{\textsf{\textbf{Example \theexample }} \hspace*{1pt} #1 %
	}}
\newcommand{\eoe}{\hfill $\square$}
\newcommand{\teoe}{\tag*{$\square$}}

\newcommand{\keypoint}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\cmt}{\noindent\hspace{-0.4em}\ding{43} \hspace{0.4em}}

% indentation and line spacing in itemize environment
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\everymath{\displaystyle}

% indentation of paragraphs and table of contents
\setlength{\parindent}{1.2em}

% columns with customised width in tabulars
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{D}[1]{ >{\centering\arraybackslash} m{1cm} }

\title{Further Mechanics}
\author{Yuhao Yang}

\newcommand{\dd}{\mathrm{d}}
\newcommand{\opdt}{\frac{\mathrm{d}}{\mathrm{d}t}}
\newcommand{\ddt}[1]{\frac{\mathrm{d}#1}{\mathrm{d}t}}
\newcommand{\dddt}[1]{\frac{\mathrm{d}^2#1}{\mathrm{d}t^2}}
\newcommand{\RA}{\quad \Rightarrow \quad}
\newcommand{\mps}{\text{ (m s$^{-1}$)}}
\newcommand{\mpss}{\text{ (m s$^{-2}$)}}
\newcommand{\tmax}{\text{max}}
\newcommand{\tmin}{\text{min}}
\newcommand{\rad}{\text{ rad}}
\newcommand{\radps}{\text{ (rad s$^{-1}$)}}
\newcommand{\eqskip}{\hspace{2.0em}}
\newcommand{\yskip}{\vspace{0.6em}}

\begin{document}
	

\vspace*{5pt}

\begin{center}
	{
		\Huge Further Mechanics
	
	}
	
	{
		\Large Yuhao Yang
		
		Easyday Education
	
	}

	
\end{center}

\vspace*{5pt}

\setcounter{page}{1}
\pagenumbering{roman} 
\tableofcontents
%\listoffigures

\newpage

\section*{A Few Words about the Notes}


This is a set of very concise lecture notes written for A-level further mechanics. I intend to introduce the physical concepts and principles required by the syllabus using a more mathematical approach, so that the reader may develop an appreciation of the interplay between mathematics and physics. A handful of worked examples are included to give the reader some rough idea about how exam-style questions look like and how the principles developed in the note can be applied to solve them. The complexity to type mathematical equations and draw diagrams on a computer gave me a good excuse to skip several interesting example questions.

Presumably the target audience of the notes are students studying the relevant A-Level course. If you are a student hoping for good grades in your exams, I suggest you have your hand on a lot of problems. The notes are supposed to be used as a reference only, but it is eventually by practising one can have a better understanding of the subject.

I have to admit that these notes are far from complete. I hope you enjoy reading the notes. But if you spot any mistake (as I guarantee there will be a lot), please let me know.

{

\flushright

Yuhao Yang

\url{colin.young@live.com}

\today

}


\newpage
\setcounter{page}{1}
\pagenumbering{arabic}

\include{momentum}

\include{circular-motion}

\include{simple-harmonics}

\include{rotational}

\include{equilibrium}

\include{misc}

%\newpage
%\printindex

\end{document}
